---
title: "STAT 579 Homework 4"
author: "Yifan Zhu"
date: "October 8, 2016"
output: pdf_document
---

**Problem 1**

(a) read the data
```{r, tidy=TRUE}
# read the data and take apostroph as character
senate109 <- read.table(file = "http://maitra.public.iastate.edu/stat579/datasets/senate-109.txt", sep = "\t", quote = "\"",  header = T)
```

(b) Bill type
    i. 
    ```{r}
    # remove the characters after "_"
    billtype <- sub(pattern = "_.*", replacement = "", x = senate109$bill_type_bill_name_bill_ID)
    ```
    ii. tabulate each type of bill
    ```{r}
    table(billtype)
    ```

(c) Data quality
```{r}
# the matrix
X <- as.matrix(senate109[3: ncol(senate109)]) 

# extract the diagnal elements of XX'
XX.diag <- diag(X %*% t(X))

# add the missing votes

number.senators <- XX.diag + senate109$missing_votes

#check if there is any discrepancy

prod(number.senators == ncol(senate109) - 2)
```

From the result above we can see the returned vector should be all 1. Thus there is no discrepancy.

(d)
```{r, tidy=TRUE, message= FALSE, warning= FALSE}
leader <- senate109$William.H...Bill..Frist..TN.
# create the matrix using the leader's opnion
leader.matrix <- matrix(rep(x = leader, times = ncol(X)), ncol = ncol(X))
#determine whether other senator's for/against/indifferent with the leader's choice
trend <- X * leader.matrix 
# remove the rows where the leader did not record a vote
trend <- trend[leader != 0,]
trend <- trend[, -ncol(trend)]
```
(e)
```{r, tidy=TRUE, warning= FALSE}
# count the for number in each column
fornum <- apply(X = trend == 1, MARGIN = 1, FUN = sum)
# count the against number in each column
againstnum <- apply(X = trend == -1, MARGIN = 1, FUN = sum)
# count the indifferent number in each column
indifferentnum <- apply(X = trend == 0, MARGIN = 1, FUN = sum)

trendcount <- data.frame(bill_type = billtype[leader != 0], for_number = fornum, against_number = againstnum, indifferent_number = indifferentnum)


# using aggregate calculating the mean for each bill type
treandcount.mean <- aggregate(trendcount, by = list(trendcount$bill_type), FUN = mean)[-2]
treandcount.mean
```

\newpage

**Problem 2**

(a) Read the data as matrix
```{r, message=FALSE, tidy=TRUE}
PET <- matrix(scan(file ="http://maitra.public.iastate.edu/stat579/datasets/fbp-img.dat"), ncol = 128, nrow = 128, byrow = T)

```

(b) image the plot
```{r, fig.align='center', fig.width=5, fig.width=5}
image(1:128, 1:128, PET[, 128:1], col = topo.colors(128^2))

```

(c)
    i.
    ```{r, fig.align='center', fig.width=5, fig.width=5}
    range <- max(PET) - min(PET)
    bin <- seq(min(PET), max(PET), length.out = 9)
    # vector of the mid points
    bin.mid <- (bin[-1] + bin[- length(bin)]) / 2
    
    # function to determine which bin is the value x in and return the mid point
    deterbin <- function(x){
      y <- bin.mid[(bin[-1] > x)&((bin[-length(bin)] < x))]
      return(y)
    }
    PET_new1 <- apply(PET, MARGIN = c(1,2), FUN = deterbin)
    mode(PET_new1) <- 'numeric'
    
    image(1:128, 1:128, PET_new1[, 128:1], col = topo.colors(128^2))
    ```
    
    ii. 
    ```{r, fig.align='center', fig.width=5, fig.width=5}
    qtbin <- quantile(PET, probs = seq(0, 1, length = 9))
    # vector of the mid points
    qtbin.mid <- (qtbin[-1] + qtbin[- length(qtbin)]) / 2
    
    # function to determine which quantile bin is the value x in and return the mid point
    deterqtbin <- function(x){
      y <- qtbin.mid[(qtbin[-1] > x)&((qtbin[-length(qtbin)] < x))]
      return(y)
    }
    PET_new2 <- apply(PET, MARGIN = c(1,2), FUN = deterqtbin)
    mode(PET_new2) <- 'numeric'
    
    image(1:128, 1:128, PET_new2[, 128:1], col = topo.colors(128^2))
    ```
    
    iii. Comment: These two methods can both discribe the image, but in the detail of the background, the method of quantile bin is better. In my opinion, using quantile bin is better. This method reflects the concentration of data and can discribe the image better.
    
\newpage

**Problem 3**

(a) read the data
```{r}
auto <- read.table(file = "C:/Users/fanne/Desktop/STAT579/Auto.txt", header = T)
```

(b) 
```{r}
X <- matrix(c(auto$horsepower, rep(1, length(auto$horsepower))), ncol = 2)
Y <- auto$mpg

beta_hat <- solve(t(X) %*% X) %*% t(X) %*% Y
beta_hat
```

(c)
```{r}
lmbeta <- lm(formula = mpg ~ horsepower, data = auto)
summary(lmbeta)
```
The result of these two methods are similar. 
