---
title: "STAT 579 Homework 7"
author: "Yifan Zhu"
date: "November 3, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy = TRUE, warning = FALSE, fig.align= "center", fig.width = 5, fig.height = 5)
```


**Problem 1**

```{r}
tridiag <- function(k,n){
  A <- matrix(rep(0, n*n), ncol = n)
  diag(A) <- rep(k, n)
  diag(A[-1,-n]) <- rep(1, n-1)
  diag(A[-n,-1]) <- rep(1, n-1)
  return(A)
}

tridiag(n = 6, k = 5)
```

\newpage

**Problem 2**

```{r}
tmpFn <- function(xVec){
  x <- xVec
  ifelse(x < 0, x^2 + 2 * x + 3, ifelse(x<2, x+3, x^2 + 4*x - 7))
}
x <- seq(-3, 3, 0.1)
fx <- tmpFn(x)

plot(x = x, y = fx, "l", col = "blue", xlab = "x", ylab = "f(x)")
```

\newpage

**Problem 3**

```{r}
gcd <- function(m, n){
  re <- m%%n
  while(re != 0){
    m <- n
    n <- re
    re <- m%%n
  }
  return(n)
}

gcd(60,130)
```

\newpage

**Problem 4**

```{r}
order.matrix <- function(x){
  dimx <- dim(x)
  ord <- order(x)
  n <- length(ord)
  dim(ord) <- dimx
  indices <- NULL
  for (i in 1:n){
    indice <- which(ord == i, arr.ind = T)
    indices <- rbind(indices, indice)
  }
  indices <- cbind(1:n, indices)
  colnames(indices) <- c("order", "row", "column")
  return(indices)
}

x <- matrix(rchisq(n = 4*3, df = 1), ncol = 3)

order.matrix(x)
```


\newpage

**Problem 5**

(a)

```{r}
polaroid <- function(x){
  p <- length(x)
  q <- rep(0, p-1)
  R <- sqrt(sum(x^2))
  q[p-1] <- ifelse(atan(x[p]/x[p-1]) >= 0, atan(x[p]/x[p-1]), atan(x[p]/x[p-1]) + pi)
  for (i in (p-2):2){
    arctan <- atan((x[i+1]/cos(q[i+1]))/x[i])
    q[i] <- ifelse(arctan >= 0, arctan, arctan + pi)
  }
  q[1] <- ifelse(x[2]/cos(q[2]) >= 0, atan2(y = x[2]/cos(q[2]), x = x[1]), atan2(y = x[2]/cos(q[2]), x = x[1]) + 2*pi)
  
  return(c(R, q))
}
```

(b)
```{r}
normalize <- function(X){
  norm <- sqrt(apply(X^2, MARGIN = 1, FUN =  sum))
  sweep(X, MARGIN = 1, STAT = norm, FUN = "/")
}
```

(c)
```{r}
y <- matrix(rnorm(n = 1000*5), ncol = 5)

z <- normalize(y)

kstest <- apply(z, MARGIN = 2 ,FUN = ks.test, "punif",min=-1,max=1)

kstest

```

P-values are small, so they should not follow the uniform distribution on $(-1,1)$.

(d)

```{r, fig.width = 12, fig.height = 3}
polar <- apply(y, MARGIN = 1, FUN = polaroid)

R2 <- (polar[1,])^2

ks.test(R2, "pchisq", df = 5)

theta <- polar[-1,]

par(mfrow = c(1,4))

hist(theta[1,], xlab = "theta1", freq = F, main = "")
hist(theta[2,], xlab = "theta2", freq = F, main = "")
hist(theta[3,], xlab = "theta3", freq = F, main = "")
hist(theta[4,], xlab = "theta4", freq = F, main = "")

ks.test(theta[1,], "punif", min = 0, max = 2*pi)

ks.test(theta[2,], "punif", min = 0, max = pi)
ks.test(theta[3,], "punif", min = 0, max = pi)
ks.test(theta[4,], "punif", min = 0, max = pi)

```

P-value for test for $R^2$ is large, so it shoould follow the $\chi_5^2$. P-value for $\theta_1, \theta_2, \theta_3$ are small, so they should not follow uniform distribution. P-value for $\theta_4$ is large, thus it should follow the uniform distribution on $[0, \pi)$.

\newpage

**Problem 6**

(a)

```{r}
x <- c(3.91,4.85, 2.28, 4.06, 3.70, 4.04, 5.46, 3.53, 2.28, 1.96, 2.53, 3.88, 2.22, 3.47, 4.82,
2.46, 2.99, 2.54, 0.52, 2.50)

l <- function(theta,x){
  n <- length(x)
  -n*log(2*pi) + sum(log(1-cos(x - theta)))
}

theta <- seq(-pi, pi, 0.01)

ltheta <- apply(t(theta), MARGIN = 2, FUN = l, x = x)

plot(x = theta, y = ltheta, "l", col = "blue", xlab = "theta", ylab = "l(theta)", main = "")
```

(b)

```{r}
thetamin <- optimize(f = l, x = x, interval = c(-pi, pi), maximum = T)

thetamin
```

(c)
```{r}
options(digits = 20)

newton <- function(fun, derf, x0, eps)
{
iter <- 0
repeat {
iter <- iter + 1
x1 <- x0 - fun(x0) / derf(x0)
if (abs(x0 - x1) < eps || abs(fun(x1)) < 1e-10)
break
x0 <- x1
cat('****** Iter. No: ', iter, ' Current Iterate = ', x1,fill=T)
}
return(x1)
}

derl <- function(theta){
  sum(sin(x - theta)/(1 - cos(x - theta)))
}

dderl <- function(theta){
  - sum(1/(1 - cos(x - theta)))
}

newton(fun = derl, derf = dderl, x0 = 0, eps = 1e-4)
```

(d)
```{r}
newton(fun = derl, derf = dderl, x0 = -2, eps = 1e-4)

newton(fun = derl, derf = dderl, x0 = -2.7, eps = 1e-4)
```

The results are different with different initial point. It is because Newton method will end with it finds a point with zero value which is nearest to the starting point. And the function has many points when its derivative is 0.
