---
title: "STAT 579 Final"
author: "Yifan Zhu"
date: "November 12, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 5, fig.height = 5, fig.align = "center")
```

**Problem 1**

(a)
```{r}
sleep <- read.table(file = "sleep.dat")

hour <- sleep$V1

circ.mean <- function(data, input.type){

  circ.mean.rad <- function(data){
    x <- cos(data)
    y <- sin(data)
    xbar <- mean(x)
    ybar <- mean(y)
    r <- sqrt(xbar^2 + ybar^2)
    cbar <- xbar/r
    sbar <- ybar/r
    
    thetabar <- atan2(y = sbar, x = cbar)
    ifelse(thetabar >= 0, thetabar, thetabar + 2*pi)
  }
  
  
  if (input.type == "radian"){
    circ.mean.rad(data)
  } else {
    if (input.type == "degree"){
      data <- degree * pi / 180
      degreebar.rad <- circ.mean.rad(data)
      degreebar <- degreebar.rad * 180 / pi
      degreebar
    } else {
      if (input.type == "hour"){
        data <- data * pi / 12
        hourbar.rad <- circ.mean.rad(data)
        hourbar <- hourbar.rad * 12 / pi
        hourbar
      } else {
        cat("****** Wrong input.type ******")
      }
    }
  }
}
```

(b)
```{r}
  display.average <- function(data, col, pch, ...){
    theta <- data * pi /12
    x <- cos(theta)
    y <- sin(theta)
    hourbar <- circ.mean(data = data, input.type = "hour")
    hourbartheta <- hourbar * pi /12
    xhourbar <- cos(hourbartheta)
    yhourbar <- sin(hourbartheta)
    
    plot(x = x, y = y, xlim = c(-1.3, 1.3), ylim = c(-1.3, 1.3), col = col[1], pch = pch[1], xlab = "", ylab = "" , ...)
    text(x = x, y = y, data, col = col[1], cex = 0.6, pos = 4)
    points(x = xhourbar, y = yhourbar, col = col[2], pch = pch[2], ...)
    text(x = xhourbar, y = yhourbar, hourbar, col = col[2], pch = pch[2], cex = 0.6, pos = 1)
  }

display.average(data = hour, col = c("blue", "red"), pch = c(1,4))

display.average(data = hour, col = c("green", "black"), pch = c(2,5))

```


(c)
    (i)
    ```{r}
    fhour <- function(hour, mu, kappa, log = FALSE){
      theta <- hour * pi / 12
      thetamu <- mu * pi / 12
      f <- exp(kappa * cos(theta - thetamu)) / (2 * pi * besselI(kappa, nu = 0))
      if (!log) f else log(f)
    }
    ```
    
    (ii)
    ```{r}
    # the log likelihood function l
    l <- function(hour, mu, kappa){
      sum(fhour(hour = hour, mu = mu, kappa = kappa, log = T))
    }
    
    # estimate the parameter mu (in hour)
    
    mu <- circ.mean(hour, input.type = "hour")
    
    mu
    
    kappa <- optimize(f = l, mu = mu, hour = hour, maximum = T, interval = c(0.001, 1000), lower = 0.001)
    
    kappa
    ```
    
    (iii)
    A. 
    ```{r}
    rVM <- function(mu, kappa, n){
      nuC <- cos(mu)
      nuS <- sin(mu)
      sigma <- 1 / sqrt(kappa)
      X <- rnorm(n = n*2, mean = 0, sd = 1)
      dim(X) <- c(n,2)
      
      X <- X * sigma
      
      X[,1] <- X[,1] + nuC
      X[,2] <- X[,2] + nuS
      
      
      
      
      atan2(X[,2], X[,1])
    }
    ```
    
    B.
    ```{r}
    thetabar <- circ.mean(hour, input.type = "hour")*pi/12
    teststat <- cos(thetabar - 0)
    teststat
    ```
    
    C. 
    ```{r}
    kappahat <- kappa$maximum
    
    B <- 1000
    
    simulationnum <- rep(0, B)
    
    simulation <- lapply(simulationnum, FUN =rVM,  kappa = kappahat, n = 100)
    
    teststat.sample <- lapply(simulation, FUN = function(x) cos(circ.mean(data = x, input.type = "radian") - 0))
    
    pvalue <- sum(unlist(teststat.sample) > teststat)/B
    
    pvalue
    ```
    
    The p-value is larger than $5 \%$, thus there is evidence that the true mean direction $\mu = 0$.
    
\newpage

**Problem 2**

(a)
```{r, fig.width = 8, fig.height= 6}
score <- read.csv(file = "brenda.csv")

plot(x = score$Time, y = score$Time , ylim = c(0.5, 0.8), "n", xlab = "Time", ylab = "Score")

lines(x = score$Time, y = score$Trained, col = "red", pch = 20, lty = 1, type = "b")

lines(x = score$Time, y = score$Repeated, col = "blue", pch = 18, lty = 1, type = "b")

apply(score, MARGIN = 1, FUN = function(x) lines(x = c(x[1], x[1]), y = c(x[2],x[3]), lty = 2))

legend(2, 0.55, c("Trained", "Repeated"), col = c("red","blue"), pch = c(20, 18), lty = 1)
```

(b)
```{r}
logit <- data.frame(Time = score$Time, Trained = log(score$Trained/(1 - score$Trained)), Repeated = log(score$Repeated/(1 - score$Repeated)))
```

(c)
```{r}
diff <- logit$Trained - logit$Repeated

logit <- data.frame(logit, Difference = diff)

lmest <- lm(formula = Difference ~ Time, data = logit)

summary(lmest)

plot(x = lmest$fitted.values, y = rstudent(lmest), xlab = "Fitted Value", ylab = "Studentized Residual")

require(graphics)
qqnorm(rstudent(lmest))
```

Time is significant in this model. The r-squared is around $30 \%$, which is not very large.



The residuals seem to be smaller for the fitted values in $(-0.1, 0.2)$ than those for the fitted values in $(0.25, 0.45)$. The regression model is not so good for the data. And according to the Q-Q Plot the residuals are not normally distributed.
    
